---
title: "IBDA_Chebyshev_logic"
author: "Justin"
date: "2022/5/8"
output: html_document
---

```{r}
library(dplyr)
library(corrplot)
```

# Data Overview

The data has been processed when conducting the decision tree, which change all the qualitative data to the integer and remove the data without ranking. Besides, we also remove the data which is meaningless, for example id and constant data.

```{r}
data <- read.csv("HR_data.csv")
data <- data[,-1]
data <- subset(data,select = -c(Attrition))
data
```

# Select the integer column

```{r}
colnames <- colnames(data)
colnames
```

# Chebyshev

Testing for the Chebyshev

```{r}
# testing for signle 
colname <- 'Age'
vector <- data[[colname]]
mean_size <- mean(vector)
sd_size <- sd(vector)
in_2nd <- vector[vector<(mean_size+2*sd_size) & vector>(mean_size-2*sd_size)]
in_3rd <- vector[vector<(mean_size+3*sd_size) & vector>(mean_size-3*sd_size)]
rate_2nd <- length(in_2nd)/length(vector)
rate_3rd <- length(in_3rd)/length(vector)
rate_2nd
rate_3rd
if_reach_2nd <- (rate_2nd>0.75)
if_reach_3rd <- (rate_3rd>0.89)
if_reach_2nd
if_reach_3rd
```

For everything

```{r}
if_2nd_list <- numeric(length(colnames))
if_3rd_list <- numeric(length(colnames))
two_rd_list <- numeric(length(colnames))
three_rd_list <- numeric(length(colnames))
for(col_ind in c(1:length(colnames))){
    colname <- colnames[col_ind]
    vector <- data[[colname]]
    mean_size <- mean(vector)
    sd_size <- sd(vector)
    in_2nd <- vector[vector<(mean_size+2*sd_size) & vector>(mean_size-2*sd_size)]
    in_3rd <- vector[vector<(mean_size+3*sd_size) & vector>(mean_size-3*sd_size)]
    rate_2nd <- length(in_2nd)/length(vector)
    rate_3rd <- length(in_3rd)/length(vector)
    rate_2nd
    rate_3rd
    if_reach_2nd <- (rate_2nd>0.75)
    if_reach_3rd <- (rate_3rd>0.89)
    if_2nd_list[col_ind] <- if_reach_2nd 
    if_3rd_list[col_ind] <- if_reach_3rd
    two_rd_list[col_ind] <- rate_2nd
    three_rd_list[col_ind] <- rate_3rd
}
#if_2nd_list
#if_3rd_list
df <- data.frame(rate_2nd=two_rd_list,if_2nd_list=if_2nd_list,rate_3rd=three_rd_list,if_3rd_list=if_3rd_list)
rownames(df) <- colnames
df
```

# Logistic regression

## Step select

```{r}
# change the position of column
data <- data %>% select(OverTime, Age,everything())
data
```

```{r}
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))

M = cor(data, method = "spearman")

corrplot(M, 
         method = "shade", 
         type = {"lower"}, 
         shade.col = NA, 
         tl.col = "black", 
         tl.srt = 45,
         tl.cex = 0.6,
         col = col(200),
         cl.pos = NULL)
```

For everything

```{r}
fit_glm <- glm(OverTime~., data = data, family = "binomial")
summary(fit_glm)
```

```{r}
fit_step_glm <- step(glm(OverTime~., data = data, family = "binomial"))
summary(fit_glm)
```

| SColname                 | Deviance | AIC    |
|--------------------------|----------|--------|
| \<none\>                 | 1718.0   | 1736.0 |
| JobRole                  | 1720.7   | 1736.7 |
| Gender                   | 1721.2   | 1737.2 |
| NumCompaniesWorked       | 1721.5   | 1737.5 |
| RelationshipSatisfaction | 1721.7   | 1737.7 |
| Age                      | 1721.7   | 1737.7 |
| YearsWithCurrManager     | 1722.7   | 1738.7 |
| EnvironmentSatisfaction  | 1725.2   | 1741.2 |
| TrainingTimesLastYear    | 1728.2   | 1744.2 |

## Select Manually

```{r}
# select the coloumns which is obtain from the step
data_sign<- subset(data, select=c(OverTime,Age,YearsWithCurrManager,TrainingTimesLastYear,EnvironmentSatisfaction,RelationshipSatisfaction,NumCompaniesWorked,Gender,JobRole))

data_sign_rank <- data_sign %>% select(OverTime, everything())
```

```{r}
fit_glm <- glm(OverTime ~ ., data = data_sign_rank, family = "binomial")
summary(fit_glm)
```

```{r}
fit_glm_b <- glm(OverTime ~ Age+YearsWithCurrManager+TrainingTimesLastYear+EnvironmentSatisfaction+RelationshipSatisfaction+NumCompaniesWorked+Gender, data = data, family = "binomial")
summary(fit_glm_b)
```

```{r}
fit_glm_b <- glm(OverTime ~ Age+YearsWithCurrManager+TrainingTimesLastYear+EnvironmentSatisfaction+NumCompaniesWorked, data = data, family = "binomial")
summary(fit_glm_b)
```

```{r}
fit_glm_b <- glm(OverTime ~ YearsWithCurrManager+TrainingTimesLastYear+EnvironmentSatisfaction+NumCompaniesWorked, data = data, family = "binomial")
summary(fit_glm_b)
```

```{r}
fit_glm_b <- glm(OverTime ~ TrainingTimesLastYear+EnvironmentSatisfaction, data = data, family = "binomial")
summary(fit_glm_b)
```

```{r}
# split the training set and testing set
index <-  sort(sample(nrow(data_sign_rank), nrow(data_sign_rank)*.9))
train <- data_sign_rank[index,]
test <-  data_sign_rank[-index,]
dim(train)
dim(test)
```

```{r}
fit_glm_b <- glm(OverTime ~ EnvironmentSatisfaction + TrainingTimesLastYear, data = train, family = "binomial")
summary(fit_glm_b)
```

```{r}
trn_pred <- ifelse(predict(fit_glm_b, newdata=test,type="response") > 0.5, 1, 0)
trn_tab <- table(predicted = trn_pred, actual = test$OverTime)
#trn_tab
print("The accuarcy is:")
sum(diag(trn_tab))/sum(trn_tab)
```

```{r}
anova(object=fit_glm_b,test = "Chisq")
```

```{r}
library(car)
data.frame(vif(fit_glm_b,digits=0))
```

```{r}
library(pROC)
prob <- predict(fit_glm, newdata=test,type="response") + 0.1
roc_curve <- roc(test$OverTime,prob)
#names(roc_curve)
x <- 1-roc_curve$specificities
y <- roc_curve$sensitivities

library(ggplot2)
p <- ggplot(data = NULL, mapping = aes(x= x, y = y))+
    geom_line(colour = 'red') + 
    geom_abline(intercept = 0, slope = 1)+
    annotate('text', x = 0.4, y = 0.5, label = paste('AUC=',round(roc_curve$auc,2)))+
    labs(x = 'Specificities',y = 'Sensitivities', title = 'ROC Curve')
p
```
